Les besoins en éducation pour les pratiques opensource

### 2022-02-11 main.tex
preamble: allow to include svg files
preamble: add shortcut command for short english texts
Build: suppress some compilation warnings

@@

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\usepackage{csquotes}

>>>>

% Suppress some compilation warnings
\RequirePackage[save,showerrors]{silence}
\WarningFilter{biblatex}
  {The starred command '\DeclareDelimAlias*' is} % APA package is using this deprecated starred version
\WarningFilter{transparent}
  {Loading aborted} % I can't find where it is loaded, probably somewhere in kao's cls or sty
\WarningFilter{latex}
  {Unused global option} % They are, but kaobook is silently passing them to its base class

@@

% Main and default language is french but there are some parts in english
\usepackage[main=french,english]{babel}
\newcommand{\english}[1]{\foreignlanguage{english}{\itshape #1}}
\usepackage{csquotes}

% Allow to include SVG with \includesvg similarly to \includegraphics for other image formats
\usepackage[inkscapepath=./build/svg-inkscape/]{svg}
